**Measuring Depression and Anxiety with 4 items? Adaptation of the PHQ-4 to increase its Sensitivity to Subclinical Variability**

### 2025-05-07 paper/4_PsychiatryResearch/manuscript.qmd
add stuff
fixed typo

shorttitle: "Short Title in Running Header"

@@

@@

While the scale has been validated and used in the general population and non-clinical samples [@lowe20104; @hajek2020prevalence], its initial purpose was to reliably discriminate and identify potential MDD/GAD patients. This discriminative goal materializes in the scale's design and the existence of categorical cut-offs, which does not necessary entail a focus on the sensitivity to milder mood alterations. In particular, the gap between the two lowest possible answers, "Not at all" and "Several days", is quite large and possibly leaves out the possibility of more subtle occurrences. While this is not necessarily an issue in clinical and diagnostic contexts, it might lead to a sub-optimal discrimination of affective levels on the lower end of the spectrum, important for instance in the context of subclinical variability quantification.

>>>>

shorttitle: "Adaptation of the PHQ-4"

@@

    keep-tex: true

@@

While the scale has been validated and used in the general population and non-clinical samples [@lowe20104; @hajek2020prevalence], its initial purpose was to reliably discriminate and identify potential MDD/GAD patients. This discriminative goal materializes in the scale's design and the existence of categorical cut-offs, which does not **necessarily** entail a focus on the sensitivity to milder mood alterations. In particular, the gap between the two lowest possible answers, "Not at all" and "Several days", is quite large and possibly leaves out the possibility of more subtle occurrences. While this is not necessarily an issue in clinical and diagnostic contexts, it might lead to a sub-optimal discrimination of affective levels on the lower end of the spectrum, important for instance in the context of subclinical variability quantification.
